Prediction of Periprosthetic Joint Infection after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden and Denmark

### 2021-01-19 reports/article.Rmd
Include T846F in inclusion list
Fix #37 OBS! Denna output hör ihop med cache_T846F som inte versionshanteras!

---
title: "Prediction of Periprosthetic Joint Infection after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden and Denmark"
author: Erik Bulow,^1,2^ Alma Besic Pedersen,^3^ Ina Trolle Andersen,^4^ Ola Rolfson,^1,2^  Nils P. Hailer^5^
date: '`r Sys.Date()`'
bibliography: 
#  H:/zotero_lib.bib
  C:\\Users\\erik_\\Documents\\library.bib
csl: the-lancet.csl
output: 
  bookdown::word_document2:
    reference_docx: article.dotx
    toc: false
    df_print: kable
---

@@

Logistic LASSO regression was performed for each sample using the chosen $\lambda_i$ as penalty term. Regression coefficients were ranked based on their absolute values as a measure of variable importance. We then used Bayesian methods to estimate a posterior distribution and to identify two change points in a linear segmented piecewise regression model. The second change point was then used as a break-point. Influential predictors with absolute coefficients value above this point, scored a point. The whole process, each with 100 Bootstrap replicates, was repeated 100 times (yielding 10,000 bootstrap samples in total). Potential predictors that were selected at least `r brlasso_selection_n["main"]` out of 100 times were then used in main effects multivariable logistic regression models without penalty and without pre-normalization of numeric variables. Even more parsimonious models with potential predictors chosen at least `r brlasso_selection_n["reduced"]` out of 100 times were evaluated for comparison. Univariable prediction models based on either ASA class, the Charlson, Elixhauser, or the Rx Risk V comorbidity indices were fitted for comparison. Odds ratios for the final models were estimated with 95 % confidence intervals.

>>>>

---
title: "Prediction of Periprosthetic Joint Infection after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden and Denmark"
author: Erik Bulow,^1,2^ Alma Besic Pedersen,^3^ Ina Trolle Andersen,^4^ Ola Rolfson,^1,2^  Nils P. Hailer^5^
date: '`r Sys.Date()`'
bibliography: 
#  H:/zotero_lib.bib
  C:\\Users\\erik_\\Documents\\library.bib
csl: the-lancet.csl
output: 
  bookdown::word_document2:
    number_sections: false
    reference_docx: article.dotx
    toc: false
    df_print: kable
---

@@

Logistic LASSO regression was performed for each sample using the chosen $\lambda_i$ as penalty term. Regression coefficients were ranked based on their absolute values as a measure of variable importance. We then used Bayesian methods to estimate a posterior distribution and to identify two change points in a linear segmented piecewise regression model. The second change point was then used as a break-point. Influential predictors with absolute coefficients value above this point, scored a point. The whole process, each with 100 Bootstrap replicates, was repeated 100 times (yielding 10,000 bootstrap samples in total). Potential predictors that were selected at least `r brlasso_selection_n["main"]` out of 100 times were then used in main effects multivariable logistic regression models without penalty and without pre-normalization of numeric variables. Even more parsimonious models with potential predictors chosen more than `r brlasso_selection_n["reduced"]` out of 100 times were evaluated for comparison. Univariable prediction models based on either ASA class, the Charlson, Elixhauser, or the Rx Risk V comorbidity indices were fitted for comparison. Odds ratios for the final models were estimated with 95 % confidence intervals.
